\rule{\textwidth}{4pt}\\[1em] \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm] Regularized Payoff Approximation in Discrete Space}\\[1em] \rule{\textwidth}{2pt}

### 2025-02-19 latex/article.tex
MAPE comparison

>>>>

\input{method_comparison.tex}

Table~\ref{tab:method_comparison} presents a comparative analysis of the three regularization 
methods across different regularization parameters ($\gamma$). The Mean Absolute Percentage 
Error (MAPE) is used as the primary metric for comparison, providing a scale-independent 
measure of approximation accuracy. Lower MAPE values indicate better approximation quality.

The results demonstrate that:
\begin{itemize}
    \item L2 regularization provides consistent performance across different $\gamma$ values,
    showing good stability in the approximation.
    \item L1 regularization achieves comparable accuracy while promoting sparser solutions,
    which can be advantageous for portfolio implementation.
    \item The weighted error method shows improved accuracy in regions with larger payoff
    values, as reflected in its MAPE scores, particularly for moderate regularization values.
\end{itemize}
